### 2024-12-02 README.Rmd
logo
fix README title
update README

# embedplyr: Tools for Working With Text Embeddings

@@

## About

embedplyr enables common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). It includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. [GloVe](https://nlp.stanford.edu/projects/glove/)), applying them to words, aggregating to produce text embeddings, reducing dimensionality, and more.

>>>>

# embedplyr <img src="man/figures/logo.png" align="right" height="138" alt="" />

@@

## Overview

embedplyr enables common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com).

* `load_embeddings()` loads pretrained [GloVe](https://nlp.stanford.edu/projects/glove/), [word2vec](https://code.google.com/archive/p/word2vec/), [ConceptNet Numberbatch](https://github.com/commonsense/conceptnet-numberbatch), and [fastText](https://fasttext.cc) word embedding models from Internet sources or from your working directory
* `embed_tokens()` returns the embedding for each token in a set of texts
* `embed_docs()` generates text embeddings for a set of documents
* `get_sims()` calculates row-wise similarity metrics between a set of embeddings and a given reference
* `average_embedding()` calculates the (weighted) average of multiple embeddings
* `reduce_dimensionality()` reduces the dimensionality of embeddings
* `normalize()` and `normalize_rows()` normalize embeddings to the unit hypersphere
* and more...
